Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-23 paper.tex
Use listing for showing XML (ref #15)

\documentclass{report}
\usepackage{suthesis-2e}
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{fancyvrb}
\usepackage{pgfplots}

@@

The XML below shows how the second pass of the first approach is rendered.
Notice that the render graph supports basic instancing through the {\em group}
and {\em instance} nodes.  When an instance node is visited, it simply traverses
the group it points to.  Complex behavior can be achieved with nested groups.

\begin{Verbatim}[fontsize=\small]
  <cull faces="front" />
  <framebuffer>
    <attachment usage="color" link="coords-texture-1" />
    <use program="primary-coords-program">
      <group id="intersection-group">
        <booleanAnd of="cube-1 cube-2" />
      </group>
    </use>
  </framebuffer>
  <framebuffer>
    <attachment usage="color" link="coords-texture-2" />
    <use program="secondary-coords-program">
      <instance of="intersection-group" />
    </use>
  </framebuffer>
  <cull faces="back" />
  <framebuffer>
    <attachment usage="color" link="results-texture" />
    <use program="second-pass-program">
      <uniform name="CoordsTexture1" link="coords-texture-1" />
      <uniform name="CoordsTexture2" link="coords-texture-2" />
      <uniform name="VolumeTexture1" link="volume-texture-1" />
      <uniform name="VolumeTexture2" link="volume-texture-2" />
      <uniform name="MVPMatrix" usage="modelviewprojection" />
      <instance of="intersection-group" />
    </use>
  </framebuffer>
\end{Verbatim}

>>>>

\documentclass{report}
\usepackage{suthesis-2e}
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{fancyvrb}
\usepackage{listings}
\usepackage{pgfplots}

@@

The XML in listing \ref{listing:xml-of-second-pass} shows how the second pass of
the first approach is rendered.  Notice that the render graph supports basic
instancing through the {\em group} and {\em instance} nodes.  When an instance
node is visited, it simply traverses the group it points to.  Complex behavior
can be achieved with nested groups.

\lstset{language=XML}
\lstset{markfirstintag=true}
\lstset{showstringspaces=false}
\lstset{caption=XML of second pass for first approach.}
\lstset{label=listing:xml-of-second-pass}
\begin{lstlisting}[frame=single,float]
<cull faces="front" />
<framebuffer>
  <attachment usage="color" link="coords-texture-1" />
  <use program="primary-coords-program">
    <group id="intersection-group">
      <booleanAnd of="cube-1 cube-2" />
    </group>
  </use>
</framebuffer>
<framebuffer>
  <attachment usage="color" link="coords-texture-2" />
  <use program="secondary-coords-program">
    <instance of="intersection-group" />
  </use>
</framebuffer>
<cull faces="back" />
<framebuffer>
  <attachment usage="color" link="results-texture" />
  <use program="second-pass-program">
    <uniform name="CoordsTexture1" link="coords-texture-1" />
    <uniform name="CoordsTexture2" link="coords-texture-2" />
    <uniform name="VolumeTexture1" link="volume-texture-1" />
    <uniform name="VolumeTexture2" link="volume-texture-2" />
    <uniform name="MVPMatrix" usage="modelviewprojection" />
    <instance of="intersection-group" />
  </use>
</framebuffer>
\end{lstlisting}
